\documentclass[margin]{res}
\textwidth=5.5in
% \pagestyle{empty}
\usepackage{latexsym}
\usepackage{multicol}
\usepackage{tgbonum}
\usepackage[T1]{fontenc}
\addtolength{\topmargin}{-.35in}
\addtolength{\oddsidemargin}{-.2in}
\addtolength{\textheight}{1in}
\begin{document}

\name{\ Liam Morris \\ lcm1115@rit.edu \\ \ (518) 727-1177 }

\address{{\bf Present Address} \\ 204 Goldenrod Lane \\
		Rochester, NY 14623 }

\address{{\bf \hfill Permanent Address} \\ \hfill 46 Juniper Drive \\ 
		Clifton Park, NY 12065 }
		
\begin{resume}

\section{Objective}
To obtain employment as an intern within the field of computer science during
spring and/or summer months.


\section{Education}
\emph{Rochester Institute of Technology}, Rochester, NY 14623 \\
Expecting B.S. \& M.S in Computer Science May 2014\\
Minors: Mathematics, American Sign Language \\
GPA: 3.77, PFOS: 3.91


\section{Skills}
\textbf{Programming Languages} \\
Proficient: Python, C++, Java \\
Some Experience: C\#, \LaTeX, MIPS Assembly, Scheme, Prolog

\textbf{Software} \\
Microsoft Windows, Various Linux Distributions (Fedora, Ubuntu), \\
Various Text Editors (Vim, Notepad++), Various IDEs (Eclipse, NetBeans)

\textbf{Languages} \\
American Sign Language, Basic Spanish


\section{Experience}
\textbf{Google Inc.} \\
Mountain View, California \hfill Summer 2012 \\
\emph{Engineering Practicum Intern}
\begin{itemize}
  \setlength{\itemsep}{-2pt}
  \item Implemented clustering algorithm to run on social networking corpus.
  \item Designed and created tools for analyzing clustering algorithm.
  \item Analyzed and tuned performance characteristics of clustering algorithm.
\end{itemize}

\textbf{Rochester Institute of Technology} \\
Rochester, New York \hfill 2011 - Present \\
\emph{Student Lab Instructor}
\begin{itemize}
  \setlength{\itemsep}{-2pt}
  \item Assisted in teaching Computer Science core classes.
  \item Offered tutoring hours in Computer Science tutoring center. 
\end{itemize}


\section{Projects}
\textbf{Virtual File System} \hfill Spring 2012 \\
\emph{Designed and implemented a virtual FAT16 file system to interface with
machine's actual file system.}

\textbf{Two-Player Game AI}\hfill Fall 2011 \\
\emph{Created a program that implemented four different two-player games as
well as an artificial intelligence strategy corresponding to each game.}

\textbf{Quoridor AI}\hfill Winter 2011 \\
\emph{Developed an artificial intelligence strategy for a player in the board
game Quoridor.}


\section{Activities}
Computer Science Community\hfill 2011 - Present \\
Security Practices and Research Student Association\hfill 2011 - Present \\
No Voice Zone\hfill 2010


\section{Honors}
Dean's List\hfill 2010 - Present \\
Project Lead The Way Scholarship Recipient\hfill 2010

\end{resume}
\end{document}